%!TEX encoding = UTF-8 Unicode

I am thankful to many people but first and foremost to my advisor, Dr.~Michael Taylor. I have been fortunate to have his excellent guidance and direction throughout both my undergraduate and graduate academic experiences. His passion for his work has served as an inspiration and his recommendation was very important in pushing me to continue to a masters. He has been a force of growth for me as a scientist, student, and person. Not to mention his willingness to go above what is expected of an advisor. Without his help I don’t know if I would have made it through the final sprint. 

I am also thankful for my committee members, Dr.~Kelly Fritz and Dr.~Lucas Kirschman. Their guidance and suggestions have been essential to the completion of my project. They have both also served as great instructors, helping me to grow in my knowledge of wetlands, statistics, and the research process.  

This project would likely not have come to form without Nicole Walker of the Missouri Department of Conservation and later the U.S.~Fish and Wildlife Service. Her guidance and education is what introduced me to working around nest boxes and further grew my interest in the ducks that use them. It is this that sparked my interest in researching this topic. 

I am also grateful to the Missouri Department of Conservation and especially the staff at Duck Creek Conservation Area. Their hard work has ensured the existence of excellent wildlife habitat available to projects like mine, the public, and most importantly the wildlife that rely on it.  