%!TEX encoding = UTF-8 Unicode

\begin{hangparas}{2em}{1}
	
	Armbruster, J.\,S. 1982. Wood Duck displays and pairing chronology. The Auk 99:116–122. 
	
	Bakner, D.\,L., K.\,M.\,Ringelman, and L.\,A.\,Reynolds. 2024. Wood duck nest survival and duckling recruitment is minimally affected by interspecific brood parasitism from Hooded Mergansers and Black-bellied Whistling-ducks. PLoS ONE 19:e0305899. 
	
	Bellrose, F.\,C., K.\,L.\,Johnson, and T.\,U.\,Meyers. 1964. Relative value of natural cavities and nesting houses for Wood Ducks. Journal of Wildlife Management 28:661. 
	
	Bortolotti, G.\,R., T.\,A.\,Marchant, J.\,Blas, and T.\,German. 2008. Corticosterone in feathers is a long-term, integrated measure of avian stress physiology. Functional Ecology 22:494–500. 
	
	Brasher, M.\,G., J.\,J.\,Giocomo, D.\,A.\,Azure, A.\,M.\,Bartuszevige, M.\,E.\,Flaspohler, D.\,E.\,Harrigal, B.\,W.\,Olson, J.\,M.\,Pitre, R.\,W.\,Renner, S.\,E.\,Stephens, and J.\,L.\,Vest. 2019. The history and importance of private lands for North American waterfowl conservation. Wildlife Society Bulletin 43:338–354. 
	
	Broadus, L.\,J., M.\,G.\,Hinton, T.\,P.\,Hahn, J.\,C.\,Wingfield, J.\,M.\,Eadie, and M.\,M.\,Makagon. 2025. Evaluating variation in acute stress response in captive Wood Ducks \textit{(Aix sponsa)}. General and Comparative Endocrinology 364:114687. 
	
	Christman, B.\,J., and A.\,A.\,Dhondt. 1997. Nest Predation in Black-Capped Chickadees: how safe are cavity nests? The Auk 114:769–773. 
	
	Clawson, R.\,L., G.\,W.\,Hartman, and L.\,H.\,Fredrickson. 1979. Dump nesting in a Missouri Wood Duck population. Journal of Wildlife Management 43:347–355. 
	
	Coupe, M., and F.\,Cooke. 1999. Factors affecting the pairing chronologies of three species of mergansers in southwest British Columbia. Waterbirds: The International Journal of Waterbird Biology 22:452–458. 
	
	Drobney, R.\,D., and L.\,H.\,Fredrickson. 1979. Food selection by Wood Ducks in relation to breeding status. Journal of Wildlife Management 43:109–120. 
	
	Dugger, B.\,D., L.\,C.\,Bollmann, and L.\,H.\,Fredrickson. 1999. Response of female Hooded Mergansers to eggs of an interspecific brood parasite. The Auk 116:269–273. 
	
	Dugger, K.\,M., B.\,D.\,Dugger, and L.\,H.\,Fredrickson. 1999. Annual survival rates of female Hooded Mergansers and Wood Ducks in southeastern Missouri. The Wilson Bulletin 111:1–6. 
	
	Dugger, K.\,M., and L.\,H.\,Fredrickson. 1992. Life history and habitat needs of the Wood Duck. Fish and Wildlife Leaflet 13.1.16.
	
	Eadie, J.\,M.\,A.\, F.\,P.\,Kehoe, and T.\,D.\,Nudds. 1988. Pre-hatch and post-hatch brood amalgamation in North American Anatidae: a review of hypotheses. Canadian Journal of Zoology 66:1709-1721.
	
	Fendley, T.\,T.\,1980. Incubating Wood Duck and Hooded Merganser hens killed by Black Rat Snakes. The Wilson Bulletin 92:526–527. 
	
	Foth, J.\,R., J.\,N. Straub, R.\,M. Kaminski, J.\,B. Davis, and T.\,D. Leininger. 2014. Aquatic invertebrate abundance and biomass in Arkansas, Mississippi, and Missouri bottomland hardwood forests during winter. Journal of Fish and Wildlife Management 5:243–251. 
	
	Hagy, H.\,M.,~and R.\,M.\, Kaminski. 2012. Winter waterbird and food dynamics in autumn-managed moist-soil wetlands in the Mississippi Alluvial Valley. Wildlife Society Bulletin 36:512–523.
	
	Hagy, H.\,M., S.\,C.\,Yaich, J.\,W.\,Simpson, E.\,Carrera, D.\,A.\,Haukos, W.\,C.\,Johnson, C.\,R.\,Loesch, F.\,A.\,Reid, S.\,E.\,Stephens, R.\,W.\,Tiner, B.\,A.\,Werner, and G.\,S.\,Yarris. 2014. Wetland issues affecting waterfowl conservation in North America. Wildfowl 2014 (Special Issue 4): 343–367. 
	
	Hamilton, W.\,J., and G.\,H.\,Orians. 1965. Evolution of brood parasitism in altricial birds. The Condor 67:361–382. 
	
	Heusmann, H.\,W., and J.\,T.\,Stolarski. 2017. Hooded Mergansers \textit{(Lophodytes cucullatus)} use nest boxes designed for Wood Ducks \textit{(Aix sponsa)}: a changing demographic. Wilson Journal of Ornithology 129:644–651. 
	
	Jalaludeen, A., R.\,R.\,Churchil, and E.\,Baéza, editors. 2022. Duck production and management strategies. Springer Nature, Singapore. 
	
	Johns, D.\,W., T.\,A.\,Marchant, G.\,D.\,Fairhurst, J.\,R.\,Speakman, and R.\,G.\,Clark. 2018. Biomarker of burden: feather corticosterone reflects energetic expenditure and allostatic overload in captive waterfowl. Functional Ecology 32:345–357. 
	
	Johnsgard, P.\,A. 1961. The sexual behavior and systematic position of the Hooded Merganser. Papers in Ornithology 9:227–236.
	
	Lacki, M.\,J., S.\,P.\,George, and P.\,J.\,Viscosi. 1987. Evaluation of site variables affecting nest box use by Wood Ducks. Wildlife Society Bulletin 15:196–200. 
	
	Landers, J.\,L., T.\,T.\,Fendley, and A.\,S.\,Johnson. 1977. Feeding ecology of Wood Ducks in South Carolina. Journal of Wildlife Management 41:118–127. 
	
	Legendre, P.\, and L. Legendre. 1998. Numerical Ecology. Second English edition. Developments in Environmental Modeliing 20. Elsevier Science B.V., Amsterdam.
	
	Liu, G., L.\,Zhou, B.\,Li, and L.\,Zhang. 2014. The complete mitochondrial genome of \textit{Aix galericulata} and \textit{Tadorna ferruginea:} bearings on their phylogenetic position in the Anseriformes.
	
	Livezey, B.\,C. 1995. Phylogeny and evolutionary ecology of modern seaducks (Anatidae: Mergini). The Condor 97:233–255. 
	
	Ludt, K.\,S. 2003. The reproductive success of the Hooded Merganser \textit{(Lophodytes cucullatus)} at Mosquito Creek Wildlife Management Area. M.\,S.\,Thesis. Youngstown State University, OH.
	
	Mallory, M.\,L., D.\,K.\,McNicol, R.\,A.\,Walton, and M.\,Wayland. 1998. Risk–taking by incubating Common Goldeneyes and Hooded Mergansers. The Condor 100:694–701. 
	
	Mallory, M.\,L., A.\,Taverner, B.\,Bower, and D.\,Crook. 2002. Wood Duck and Hooded Merganser breeding success in nest boxes in Ontario. Wildlife Society Bulletin 30:310–316. 
	
	McNicol, D.\,K., R.\,A.\,Walton, and M.\,L.\,Mallory. 1997. Monitoring nest box use by cavity-nesting ducks on acid-stressed lakes in Ontario, Canada. Wildlife Biology 3:1–12. 
	
	Morse, T.\,E., J.\,L.\,Jakabosky, and V.\,P.\,McCrow. 1969. Some aspects of the breeding biology of the Hooded Merganser. Journal of Wildlife Management 33:596–604. 
	
	Nichols, J.\,D., F.\,A.\,Johnson, and B.\,K.\,Williams. 1995. Managing North American Waterfowl in the face of uncertainty. Annual Review of Ecology and Systematics 26:177–199. 
	
	Nichols, J.\,D., M.\,C.\,Runge, F.\,A.\,Johnson, and B.\,K.\,Williams. 2007. Adaptive harvest management of North American waterfowl populations: a brief history and future prospects. Journal of Ornithology 148:343–349. 
	
	Norton, M.\,R., and V.\,G.\,Thomas. 1994. Economic analyses of ‘crippling losses’ of North American waterfowl and their policy implications for management. Environmental Conservation 21:347–353. 
	
	Oksanen, J., G.\,L.\,Simpson, F.\,G.\,Blanchet, R.\,Kindt, P.\,Legendre, P.\,R.\,Minchin, R.\,B.\,O’Hara, P.\,Solymos, M.\,H.\,H.\,Stevens, E.\,Szoecs, H.\,Wagner, M.\,Barbour, M.\,Bedward, B.\,Bolker, D.\,Borcard, G.\,Carvalho, M.\,Chirico, M.\,D.\,Caceres, S.\,Durand, H.\,B.\,A.\,Evangelista, R.\,FitzJohn, M.\,Friendly, B.\,Furneaux, G.\,Hannigan, M.\,O.\,Hill, L.\,Lahti, D.\,McGlinn, M.-H.\,Ouellette, E.\,R.\,Cunha, T.\,Smith, A.\,Stier, C.\,J.\,F.\,Ter Braak, J.\,Weedon, and T.\,Borman. 2024. vegan: Community Ecology Package. R package version 2.6-8, <https://cran.r-project.org/web/packages/vegan/index.html>. 
	
	Perry, M.\,C., A.\,M.\,Wells-Berlin, D.\,M.\,Kidwell, and P.\,C.\,Osenton. 2007. Temporal changes of populations and trophic relationships of wintering diving ducks in Chesapeake Bay. Waterbirds 30:4–16. 
	
	Pöysä, H., M.\,Milonoff, and J.\,Virtanen. 1997. Nest predation in hole-nesting birds in relation to habitat edge: an experiment. Ecography 20:329–335. 
	
	Purcell, K.\,L., J.\,Verner, and L.\,W.\,Oring. 1997. A comparison of the breeding ecology of birds nesting in boxes and tree cavities. The Auk 114:646–656. 
	
	On X. 2025. On X Hunt app for Android. https://www.onxmaps.com/hunt/app
	
	R Core Team. 2024. R: a language and environment for statistical computing. R Foundation for Stastical Computing, Vienna, Austria.  <https://www.R-project.org/>.
	
	Rabinowitz, G.\,B. 1975. An introduction to nonmetric multidimensional scaling. American Journal of Political Science 19:343–390. 
	
	Rodway, M.\,S. 2007. Timing of pairing in waterfowl I: reviewing the data and extending the theory. Waterbirds: The International Journal of Waterbird Biology 30:488–505. 
	
	Rohwer, F.\,C., and M.\,G.\,Anderson. 1988. Female-biased philopatry, monogamy, and the timing of pair formation in migratory waterfowl. Pages 187–221 in R.\,F.\,Johnston, editor. Current Ornithology. Springer US, Boston, MA. 
	
	Romero, L.\,M., and G.\,D. Fairhurst. 2016. Measuring corticosterone in feathers: strengths, limitations, and suggestions for the future. Comparative Biochemistry and Physiology Part A: Molecular \& Integrative Physiology 202:112–122. 
	
	Rosenberg, K.\,V., A.\,M.\,Dokter, P.\,J.\,Blancher, J.\,R.\,Sauer, A.\,C.\,Smith, P.\,A.\,Smith, J.\,C.\,Stanton, A.\,Panjabi, L.\,Helft, M.\,Parr, and P.\,P.\,Marra. 2019. Decline of the North American avifauna. Science 366:120–124. 
	
	Ryan, D.\,C., R.\,J.\,Kawula, and R.\,J.\,Gates. 1998. Breeding biology of Wood Ducks using natural cavities in southern Illinois. Journal of Wildlife Management 62:112–123. 
	
	Salyer, J.\,C., and K.\,F.\,Lagler. 1940. The food and habits of the American Merganser during winter in Michigan, considered in relation to fish management. Journal of Wildlife Management 4:186–219. 
	
	Scherpelz, J.\,A. 1979. Chronology of pair formation and breeding biology in the Wood Duck. M.S.\,Thesis, University of Missouri--Columbia. 
	
	Semel, B., and P.\,W.\,Sherman. 1992. Use of clutch size to infer brood parasitism in Wood Ducks. Journal of Wildlife Management 56:495–499. 
	
	SénéChal, H., G.\,Gauthier, and J.-P.\,L.\,Savard. 2008. Nesting ecology of Common Goldeneyes and Hooded Mergansers in a boreal river System. The Wilson Journal of Ornithology 120:732–742. 
	
	Silvestro, R.\,L.\,D. 2013. Audubon Wildlife Report 1987. Academic Press. 
	
	Soulliere, G.\,J., and T.\,P.\,Rusch. 1996. Nesting characteristics of Hooded Mergansers, Wood Ducks, European Starlings and Tree Swallows in Wisconsin (Características de anidamiento de \textit{Mergus cucullatus, Aix sponsa, Sturnus vulgaris} y \textit{Tachycineta bicolor} en Wisconsin). Journal of Field Ornithology 67:100–104. 
	
	Wilkins, K., and E.\,G. Cooch. 1999. Waterfowl population status, 1999. U.\,S.\,Fish \& Wildlife Publications 404. 
	
	Williams, B.\,K., M.\,D.\,Koneff, and D.\,A.\,Smith. 1999. Evaluation of waterfowl conservation under the North American Waterfowl Management Plan. Journal of Wildlife Management 63:417–440. 
	
	Zicus, M.\,C. 1990. Nesting biology of Hooded Mergansers using nest boxes. Journal of Wildlife Management 54:637–643. 
	
\end{hangparas}