%!TEX encoding = UTF-8 Unicode

\section*{Habitat}

Water levels did not fluctuate much during the study (Figures~\ref{fig:water_width_plot} and~\ref{fig:water_depth_plot}), so  modal width and depth were used for analysis.  Water width was not significantly different among the pools ($F_{2,27} = 2.87, p = 0.074$; Figure~\ref{fig:water_width_plot}). Pool~2 was the narrowest ($\overline{x} =$ \num{5.3} \unit{\meter}). Pool~1 trended wider ($\overline{x} =$ 6.4 m). Pool~3 was much wider than the other  pools on average ($\overline{x} = 11.9$ \unit{\meter}) but this was due to boxes S20 and S34 (Figure~\ref{fig:nest_box_map}) that were located along a broad, shallow pool. Most other nest boxes in Pool~3 were along ditches with widths comparable to Pools~1 and~2  (Figure~\ref{fig:water_width_plot}). Water depth was significantly different among the 3 pools ($F_{2,27} = 4.77, p < 0.017$). Pool~1 was signficantly deeper ($\overline{x} = 1.6$ \unit{\meter}) than Pool~2 ($\overline{x} = 0.56$~\unit{\meter}) and Pool~3 ($\overline{x} = 0.74$~\unit{\meter};  Table~\ref{tab:wd_hsd_table} and Figure~\ref{fig:hsd_wd_plot}, Appendix A). Nest boxes on the west side of Pool~1 were located along a deeper and somewhat wider ditch compared to boxes on the east side of Pool~1 (Figures~\ref{fig:nest_box_map} and~\ref{fig:water_depth_plot}).  

\input{figs/water_width_plot}

\input{figs/water_depth_plot}

Tree coverage differed significantly among the 3 pools ($F_{2,20} = 6.032, p < 0.009$; Table~\ref{tab:anova_coverage}; Figure~\ref{fig:tree_coverage_plot}). Pool~1 was significantly more open ($\overline{x} = 13{,}628$ \unit{\meter\squared}) compared to Pool~2 ($\overline{x} = 25{,}176$ \unit{\meter\squared}) and Pool~3 ($\overline{x} = 23{,}669$ \unit{\meter\squared}) (Table~\ref{tab:coverage_hsd_table} and Figure~\ref{fig:hsd_coverage_plot}, Appendix A), due to the proximity of the large and open areas of Pool~1 and Unit~A. 

\input{tables/anova_coverage}

\input{figs/tree_coverage_plot}

\section*{Nesting}

Nesting events occurred in 17 of the 30 nest boxes (56.7\%) were used for nesting during the study period. A second, sequential nesting attempt occurred in 6 of those 17 boxes, for a total of 23 nests during the study period. Two attempts were made in 6 boxes for 23 total nesting events. The second attempts were treated as independent nesting events for analysis. 
Hooded Mergansers accounted for 9 nesting events and Wood Ducks accounted for the other 14 events (Tables~\ref{tab:hooded_merganser_data_table} and ~\ref{tab:wood_duck_data_table}).  Ten nesting events occurred in the Pool~2 in 7 boxes. Nine of the events were by Wood Ducks; only one was by Hooded Merganser. Nine nesting events occurred in the Pool~3 in 7 boxes. Five of the events were by from Hooded Mergansers and four were by Wood Ducks. Only 4 nesting events occurred in Pool~1 in 4 boxes. Three events were by Hooded Mergansers and only one by Wood Duck. No nests were observed in natural cavities in the vicinity of these nest boxes.  

\input{tables/hooded_merganser_data_table}

\input{tables/wood_duck_data_table}

Nesting success was based on the number of hatched eggs, including dumped eggs. Hooded Merganser hatched \numrange[range-phrase = –]{0}{18}, with a mean of \num{8.3} eggs. Wood Duck hatched \numrange[range-phrase = –]{0}{16} eggs, with a mean of \num{9.3} eggs. The number of hatched eggs was not significantly different between species ($t = -0.388, p = 0.702$). A significant interaction effect for number of eggs hatched did occur between species and pool ($F_{2,18} = 5.96, p < 0.05$; Table~\ref{tab:anova_table}). Hooded Merganser hatched a total of 42 eggs in the Pool~1 in three events compared to 43 eggs in Pool~2 (11 eggs) and Pool~3 (32 eggs) in 6 events, including 2 failed events in Pool~3 (Table~\ref{tab:hooded_merganser_data_table}; Figure~\ref{fig:hatched_eggs_plot}). Wood Ducks hatched 64 eggs in Pool~2 in 6 boxes. Three boxes were used for sequential events. The second attempts in boxes E22 and E93 both both failed. Wood Ducks hatched 54 eggs in Pool~3 across four events in three boxes. This species made only one attempt in Pool~1 and hatched just 2 eggs (Table~\ref{tab:wood_duck_data_table}; Figure~\ref{fig:hatched_eggs_plot}). 

\input{tables/anova_table}

\input{figs/hatched_eggs_plot} 

Dump nesting was observed in 3 of 9 Hooded Merganser nests (Figure~\ref{fig:dumped_eggs_plot}). Egg dumping in Hooded Merganser nests occurred in nest boxes N93, S7, and S44, with 2, 2, and 10 eggs, respectively. These are the only three Hooded Merganser nests that did not have 100\% hatching success (Table~\ref{tab:hooded_merganser_data_table}). The most extreme dump nesting event for a Hooded Merganser hen was in nest box S7. The original hen laid only 2 eggs. An additional 10 eggs were added by Wood Duck. Only one Hooded Merganser egg hatched. The second was abandoned. All 10 Wood Duck eggs hatched (Table~\ref{tab:raw_data_eggs}, Appendix A). This was the only observed event where Wood Duck dump-nested in a Hooded Merganser nest.

In comparison, dump nesting occured in 10 of 14 Wood Duck nests. The number of eggs dumped in Wood Duck nests ranged from 1–6, with a mean of 3.3 eggs. Only boxes E65, S20 attempt 2, and S14 saw fewer eggs hatched than those originally laid by the Wood Duck hen. Box E65 was the only observed instance of a Hooded Merganser egg being nest-dumped in a Wood Duck nest. For most cases, the number of eggs hatch in a nest with known dump-nesting, the number of eggs hatched matched the number of eggs laid originally by the Wood Duck hen.


\input{figs/dumped_eggs_plot} 


The relationship among hatching, water width and depth, and tree coverage was revealed by the \textsc{nmds} analysis (Figures~\ref{fig:nmds_plot_axes12} and~\ref{fig:nmds_plot_axes23}).  Both species had successful hatching for most nests (Figures~\ref{fig:nmds_plot_axes12} and~\ref{fig:hatched_eggs_plot}). Three Hooded Merganser nests were on the west side of the North section, which tended to have deeper water (Figures~\ref{fig:water_depth_plot} and~\ref{fig:nmds_plot_axes23}). Hooded Merganser had their highest number of eggs hatched in Pool~1 with nest boxes N2 and N93 (Figures~\ref{fig:hatched_eggs_plot} and~\ref{fig:nmds_plot_axes12}) although fewer eggs were hatched in nest box N47. Hooded Merganser did have success in Pool~2 and Pool~3. The only 2 failed nests for Hooded Merganser were in Pool~3, both in box S34. 

\input{figs/nmds_plot_axes12} 

\input{figs/nmds_plot_axes23} 

Most Wood Ducks nested along the relatively shallow, narrow ditches (Figure~\ref{fig:nmds_plot_axes12}) of Pool~2 and Pool~3. They established only one nest on the east side of Pool 1 where the ditch is relatively shallow and narrow. Wood Duck did have two sequential nesting attempts in Pool~3 in the nest box S20, which is located along a broad, shallow pool. Wood Duck had two failed attempts in Pool~3 in nest boxes E4 and E93 (Figures~\ref{fig:hatched_eggs_plot} and~\ref{fig:nmds_plot_axes12}). %N\textsc{mds} stress was \num{0.023}, indicating a very good fit between the data and ordination results.


